\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Section 6 revisions

\begin{figure}[!p]
  \centering
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
      \caption{}
  \end{subfigure}
  \caption{A schematic representing orthogonal and oblique reconciliations. The orange points in (a) represent in-sample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in (b) indicate potential base forecasts while the blue dot ${\hat{\bm y}}$ represents one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. (c) shows the orthogonal projection of all potential base forecasts onto the coherent subspace while (d) shows an oblique projection.} \label{fig:OthogonalVSOblique_projection}
\end{figure}

@@

\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
		\caption{Total domestic overnight trips (in logs) for Australia from January 1998 to December 2017. The top-panel shows a time plot; the bottom-left panel a sub-series plot for each month; the bottom-right panel shows a seasonal plot coloured by year.} \label{fig:Total_TSplots}
	\end{figure}

@@

The forecasts are then back-transformed by simply reversing the Box-Cox transformation using,
\begin{equation} \label{eq:BoxCox_back-transformation}
	\hat{y}_{t+h|t} =
	\begin{cases}
	\exp({\hat{w}_{t+h|t}}) & \text{if}~\lambda = 0, \\
	(\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}  & \text{otherwise.}
	\end{cases}
\end{equation}
These back-transformed forecasts are potentially biased as they are not the mean of the forecast distribution but the median (assuming that the distribution of the transformed space is symmetric). Hence, the reconciled forecasts that follow from these forecasts will also be biased. We refer to these as ``Biased'' base forecasts in the results that follow. This is the exact scenario we want to demonstrate in this study and we next move to our proposed solution of bias correcting the base forecasts before reconciling for which we explore two scenarios.

@@

\section{Conclusions} \label{sec:conclusions}

	%By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection based geometric framework. We have also established new theoretical results that support the use of projections for point forecast reconciliation. We show that projection of unbiased base forecasts onto the coherent subspace will always produce unbiased reconciled forecasts. Yet the projection-based reconciliation can be used to reconciled bias base forecasts after bias adjustments. Empirical results from the application of these methods to forecasting Australian domestic tourism flow show that reconciled forecast follows from bias-adjusted base improves the forecast accuracy and unbiased MinT reconciliation is outperforming.

	Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods.  We have also provided evidence that bias correction before reconciliation, improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation. Our intention in proposing a geometric interpretation is also to provoke research into new areas.  We now discuss three such possibilities.

	First, it should be possible to extend to the concept of coherence to non-linear constraints.  In these cases the coherent space may need to be defined by a manifold.  Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold.  Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.  Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework. The latter two are issues we investigate in separate papers.

\clearpage
	\section{Appendix} 
	%\thisfloatpagestyle{empty}
	\subsection{Proof $\bm{S}\bm{G}\bm{S}=\bm{S}$ implies $\bm{S}\bm{G}$ is a projection} \label{app:projection-proof}
	Here we establish that if $\bm{S}\bm{G}$ is a projection onto the linear subspace spanned by $\bm{S}$ then $\bm{S}\bm{G}\bm{S}=\bm{S}$.  We also prove that the converse holds, namely that if the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ holds then $\bm{S}\bm{G}$ must be a projection onto the linear subspace spanned by $\bm{S}$.

	To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$.  Since by definition, $\bm{s}_j$ lies in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$.  Stacking these vectors horizontally
	\begin{align*}
	\bm{S}\bm{G}\bm{S}&=\begin{pmatrix}
	\bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
	\end{pmatrix}\\
	&=\begin{pmatrix}
	\bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
	\end{pmatrix}\\
	&=\bm{S}
	\end{align*}

>>>>

\begin{figure}[!p]
  \centering
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
      \caption{}
  \end{subfigure}
  \begin{subfigure}[!h]{0.415\textwidth}
      \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
      \caption{}
  \end{subfigure}
  \caption{A schematic representing orthogonal and oblique reconciliations. The orange points in (a) represent in-sample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in (b) indicate potential base forecasts while the blue dot ${\hat{\bm y}}$ represents one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. (c) shows the orthogonal projection of all potential base forecasts onto the coherent subspace while (d) shows an oblique projection.}\label{fig:OthogonalVSOblique_projection}
\end{figure}

@@

\begin{figure}
  \centering
  \small
  \includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
  \caption{Total domestic overnight trips (in logs) for Australia from January 1998 to December 2017. The top-panel shows a time plot; the bottom-left panel a sub-series plot for each month; the bottom-right panel shows a seasonal plot coloured by year.}\label{fig:Total_TSplots}
\end{figure}

@@

The forecasts are then back-transformed by simply reversing the Box-Cox transformation using,
\begin{equation}\label{eq:BoxCox_back-transformation}
  \hat{y}_{t+h|t} =
    \begin{cases}
      \exp({\hat{w}_{t+h|t}})                   & \text{if}~\lambda = 0, \\
      (\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda} & \text{otherwise.}
  \end{cases}
\end{equation}
These back-transformed forecasts are potentially biased as they are not the mean of the forecast distribution but the median (assuming that the distribution of the transformed space is symmetric). Hence, the reconciled forecasts that follow from these forecasts will also be biased. We refer to these as ``Biased'' base forecasts in the results that follow. This is the exact scenario we want to demonstrate in this study and we next move to our proposed solution of bias correcting the base forecasts before reconciling for which we explore two scenarios.

@@

\section{Conclusions}\label{sec:conclusions}

%By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection-based geometric framework. We have also established new theoretical results that support the use of projections for point forecast reconciliation. We show that projection of unbiased base forecasts onto the coherent subspace will always produce unbiased reconciled forecasts. Yet the projection-based reconciliation can be used to reconciled bias base forecasts after bias adjustments. Empirical results from the application of these methods to forecasting Australian domestic tourism flow show that reconciled forecast follows from bias-adjusted base improves the forecast accuracy and unbiased MinT reconciliation is outperforming.

Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods. We have also provided evidence that bias correction before reconciliation improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation. Our intention in proposing a geometric interpretation is also to provoke research into new areas. We now discuss three such possibilities.

First, it should be possible to extend the concept of coherence to non-linear constraints. In these cases the coherent space may need to be defined by a manifold. Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold. Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation, an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves. Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework. The latter two are issues we investigate in separate papers.

\clearpage

\section{Appendix}

\subsection{Proof $\bm{S}\bm{G}\bm{S}=\bm{S}$ implies $\bm{S}\bm{G}$ is a projection}\label{app:projection-proof}

Here we establish that if $\bm{S}\bm{G}$ is a projection onto the linear subspace spanned by $\bm{S}$ then $\bm{S}\bm{G}\bm{S}=\bm{S}$. We also prove that the converse holds, namely that if the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ holds then $\bm{S}\bm{G}$ must be a projection onto the linear subspace spanned by $\bm{S}$.

To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$. Since by definition, $\bm{s}_j$ lies in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$. Stacking these vectors horizontally
\begin{align*}
\bm{S}\bm{G}\bm{S}
  & = \begin{pmatrix}
        \bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
      \end{pmatrix} \\
  & = \begin{pmatrix}
        \bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
      \end{pmatrix}\\
  & = \bm{S}.
\end{align*}
